Mechanization of Separation in Generic Extensions

### 2019-01-05 LICS/separation_arxiv.tex
titulo e intro

\hypersetup{
  pdftitle={Separation in Generic Extensions for Isabelle},
  pdfsubject={Computer Science},
  pdfkeywords={Isabelle/ZF, forcing, names, generic extension, constructibility},
  colorlinks,
  linkcolor={blue!40!black},
  citecolor={blue!40!black},
  urlcolor={blue!40!black}
}

\begin{document}
\title{Separation in Generic Extensions for Isabelle}
\author{Emmanuel Gunther
  \and 
  Miguel Pagano
  \and 
  Pedro S\'anchez Terraf}
\maketitle

>>>>

\hypersetup{
  pdftitle={Mechanization of Separation in Generic Extensions},
  pdfsubject={Computer Science},
  pdfkeywords={Isabelle/ZF, forcing, names, generic extension, constructibility},
  colorlinks,
  linkcolor={blue!40!black},
  citecolor={blue!40!black},
  urlcolor={blue!40!black}
}

\begin{document}
\title{Mechanization of Separation in Generic Extensions}
\author{Emmanuel Gunther
  \and 
  Miguel Pagano
  \and 
  Pedro S\'anchez Terraf}
\maketitle
